### 2022-06-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@4133488794dda87aa98a04045a49e026179857d2 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@fac76101eed06dd1ebdabb25591c7cfc5bb771a6 🚀

Species interactions are important. It is ultimately interactions
between individuals of different species that drive the structure,
dynamics, and persistence of ecosystems, and the abundance and diversity
of the species within them. Plant-pollinator interactions specifically
drive the function and persistence of ``architecture of biodiversity''
(Bascompte \& Jordano 2007). However, we are far from a robust
understanding of plant-pollinator networks. This is because sampling
interactions is costly. Interactions vary in space and time (Poisot
\emph{et al.} 2015)---particularlly relevent in this system (CaraDonna
\emph{et al.} 2014). This is why there is interest in using models to
predict interactions from sparse data (\textbf{Strydom2021?}). In this
paper, we combine several datasets, each spanning several years, to
produce spatially and temporally explicit predictions of the bumblebee
(genus \emph{Bombus}) and wildflower pollination network across the
state of Colorado.

@@

\hypertarget{data}{%
\section{Data}\label{data}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

We fit a bunch of models using MLJ.jl.

Some of them are bagged, some are not bagged.

@@

@@

@@

\textbf{\emph{Figure 3: Maps over time figure and Prob(Connectance)
vs.~Month figure}}

@@

>>>>

Ecosystems emerge from sets of interactions between pairs of species.
these interactions produce the dynamics and persistence of ecosystems,
and the abundance and diversity of the species within them.
Plant-pollinator interactions specifically drive the function and
persistence of ``architecture of biodiversity'' (Bascompte \& Jordano
2007). However, we are far from a robust understanding of
plant-pollinator networks. This is because sampling interactions is
costly. Interactions vary in space and time (Poisot \emph{et al.}
2015)---particularly relevant in this system (CaraDonna \emph{et al.}
2014). This is why there is interest in using models to predict
interactions from sparse data (\textbf{Strydom2021?}). In this paper, we
combine several datasets, each spanning several years, to produce
spatially and temporally explicit predictions of the bumblebee (genus
\emph{Bombus}) and wildflower pollination network across the state of
Colorado.

@@

\hypertarget{data-and-methodology}{%
\section{Data and methodology}\label{data-and-methodology}}

@@

@@

We fit a bunch of models using MLJ.jl. Some of them are bagged, some are
not bagged.

We train each model on each possible combination of features.

@@

\textbf{\emph{Figure 3: Embedded networks pre and post prediction a la
that virus paper}}

@@

\hypertarget{spatial-prediction}{%
\subsection{Spatial prediction}\label{spatial-prediction}}

Boosted regression tree using EvoTrees.jl, using data from GBIF.

@@

\hypertarget{temporal-prediction}{%
\subsection{Temporal prediction}\label{temporal-prediction}}

\begin{figure}
\centering
\includegraphics{./figures/ssdms.png}
\caption{todo}
\end{figure}

\textbf{\emph{Figure 5: Maps over time figure and Prob(Connectance)
vs.~Month figure}}

@@

Embedding is a good tool for x. How do we select the dimensionality of
our predictors? {[}Paper on ecological dimensionality{]}. But this
doesn't mean 7-dimensions is adaquete to describe our predictors in
models to predict species interactions.
